Impact of the 2016 Presidential Election on Urban Mobility: Who is Affected the Most?

### 2019-12-04 manuscript.Rmd
distance metric

>>>>

```{r dist_to_center}
# Compute distance from Washington Monument
mnm <- tribble(
  ~latitude, ~longitude,
  38.8895, -77.0353
)

mnm_sf <- mnm %>%
  st_as_sf(coords = c("longitude", "latitude"), crs = 4326) %>%
  st_transform(crs = 102285)

travel_time_sf <- travel_time_sf %>%
  mutate(distance = st_distance(centroids, mnm_sf$geometry, by_element = TRUE))
```
